KidsAIR: exposure model

### 2020-05-07 collinearity_exposure_analysis.Rmd
analysis updates

```{r, eval=TRUE, include=TRUE}
# Filter data for specific variables; select pm variable
pm_mean_sampling_period <- analysis_data %>% 
  select(pm_mean_sampling_period, income_3level, 
         residents_smoke,
         home_floors_2level, 
         home_pets_2level,
         chimney_clean_3level, 
         stove_cert, 
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         home_act_smoke_2level, 
         home_act_door_2level,
         stove_grade_3level) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(pm_mean_sampling_period)

# Filter data for specific variables; select predictor variables
other_vars <- analysis_data %>% 
  select(pm_mean_sampling_period, income_3level, 
         residents_smoke,
         home_floors_2level, 
         home_pets_2level,
         chimney_clean_3level, 
         stove_cert, 
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         home_act_smoke_2level, 
         home_act_door_2level,
         stove_grade_3level) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(-pm_mean_sampling_period)

>>>>

```{r, eval=TRUE, include=TRUE}
# Filter data for specific variables; select pm variable
pm_mean_sampling_period <- analysis_data %>% 
  select(pm_mean_sampling_period, 
         income_3level, 
         residents_smoke,
         home_year_built_2level,
         home_floors_2level, 
         home_pets_2level,
         stove_age_3level,
         chimney_clean_3level, 
         home_fireplace,
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(pm_mean_sampling_period)

# Filter data for specific variables; select predictor variables
other_vars <- analysis_data %>% 
  select(pm_mean_sampling_period, 
         income_3level, 
         residents_smoke,
         home_year_built_2level,
         home_floors_2level, 
         home_pets_2level,
         stove_age_3level,
         chimney_clean_3level, 
         home_fireplace,
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level) %>% 
  #mutate(area = factor(area)) %>% 
  mutate_all(as.numeric) %>% 
  filter(!is.na(pm_mean_sampling_period)) %>% 
  #na.exclude() %>% 
  select(-pm_mean_sampling_period)

### 2020-05-07 exposure_models.Rmd
analysis updates

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  #filter(area == "WMT") %>% 
  group_by(area, home) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  group_by(home) %>% 
  mutate(residents_smoke = if_else(winter_id == 1 & is.na(residents_smoke),
                                   lead(residents_smoke), residents_smoke)) %>% 
  ungroup() %>% 
  left_join(sums_temp_change, by = c("area", "home", "home_winter_id")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home", "home_winter_id")) %>% 
  replace_with_na(replace = list(mean_temp_sampling_period_5 = "NaN")) %>% 
  mutate(home_act_door_2level = cut(home_act_door, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))
```

@@

# Select analysis vars
selected_vars <- analysis_data %>% 
  #filter(area == "WMT") %>% 
  select(home, area, pm_mean_sampling_period, income_3level, 
         residents_smoke, home_floors_2level, home_pets_2level,
         chimney_clean_3level, stove_cert, wood_collect_2level,
         moisture_closest_2level, sums_events_sampling_period,
         mean_temp_sampling_period_5, amb_pm_sampling_period_5,
         home_act_smoke_2level, home_act_door_2level, stove_grade_3level) %>% 
  mutate(log_pm_mean_sampling_period = log(pm_mean_sampling_period))  
  #select(-pm_mean_sampling_period) 
```

@@

# Summary Statistics
missing_summary <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(residents_smoke), "missing yes", "missing no")) %>%
  group_by(area, missing_var) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc_miss = n/total_n*100) %>% 
  select(area, missing_var, n, perc_miss, mean_pm, sd_pm, median_pm)
missing_summary

# T-tests
missing_test <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(residents_smoke), "missing yes", "missing no")) %>% 
  filter(!is.na(log_pm_mean_sampling_period) & !is.na(missing_var))

@@

missing_summary <- complete_case %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_pm, sd_pm, median_pm)
missing_summary

@@

missing_summary <- missing_data %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_pm, sd_pm, median_pm)
missing_summary

@@

# Impute missing data; m = 10 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=10, maxit = 5,
                     method = c("polr", "logreg", "logreg", "logreg", "polr",
                                "polr", "logreg", "logreg", "pmm", "pmm",
                                "pmm", "logreg", "logreg", "polr", "pmm"))

@@

# Using MAMI package, perform model averaging and selection
## Will take ~20 to 30 mins with 5 iterations and bootstrap
model_ave <- mami(imputed_data, missing.data = "imputed", model = "gaussian",
                  outcome = "log_pm_mean_sampling_period", 
                  method = "MA.criterion", criterion = "AIC", print.time = TRUE,
                  inference = "+boot", B = 2, X.org = selected_vars)

summary(model_ave)
plot(model_ave)
```

>>>>

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  #filter(area == "WMT") %>% 
  group_by(area, home) %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 12, 100),
                                 labels = c("<12", "12+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  group_by(home) %>% 
  mutate(residents_smoke = if_else(winter_id == 1 & is.na(residents_smoke),
                                   lead(residents_smoke), residents_smoke)) %>% 
  ungroup() %>% 
  left_join(sums_temp_change, by = c("area", "home", "home_winter_id")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home", "home_winter_id")) %>% 
  replace_with_na(replace = list(mean_temp_sampling_period_5 = "NaN")) %>% 
  mutate(home_act_door_2level = cut(home_act_door, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))
```

@@

# Select analysis vars
selected_vars <- analysis_data %>% 
  filter(area == "WMT") %>% 
  select(pm_mean_sampling_period, 
         income_3level, 
         residents_smoke,
         home_year_built_2level,
         home_floors_2level, 
         home_pets_2level,
         stove_age_3level,
         chimney_clean_3level, 
         home_fireplace,
         wood_collect_2level,
         moisture_closest_2level,
         sums_events_sampling_period,
         mean_temp_sampling_period_5,
         amb_pm_sampling_period_5,
         stove_grade_3level) %>% 
  mutate(log_pm_mean_sampling_period = log(pm_mean_sampling_period)) %>% 
  select(-pm_mean_sampling_period) 
```

@@

# Summary Statistics
missing_summary <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(stove_age_3level), "missing yes", "missing no")) %>%
  group_by(area, missing_var) %>% 
  summarize(n = n(),
            mean_pm = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_pm = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_pm = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc_miss = n/total_n*100) %>% 
  select(area, missing_var, n, perc_miss, mean_pm, sd_pm, median_pm)
missing_summary

# T-tests
missing_test <- selected_vars %>% 
  mutate(missing_var = if_else(is.na(stove_age_3level), "missing yes", "missing no")) %>% 
  filter(!is.na(log_pm_mean_sampling_period) & !is.na(missing_var))

@@

missing_summary <- complete_case %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_var = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_var = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_var = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_var, sd_var, median_var)
missing_summary

missing_summary <- complete_case %>% 
  group_by(area, wood_collect_2level) %>% 
  summarize(n = n()) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc = n/total_n*100) %>% 
  select(area, wood_collect_2level, n, perc, total_n)
missing_summary

@@

missing_summary <- missing_data %>% 
  group_by(area) %>% 
  summarize(n = n(),
            mean_var = mean(pm_mean_sampling_period, na.rm = TRUE), 
            sd_var = sd(pm_mean_sampling_period, na.rm = TRUE),
            median_var = median(pm_mean_sampling_period, na.rm = TRUE)) %>% 
  group_by(area) %>% 
  select(area, n, mean_var, sd_var, median_var)
missing_summary

missing_summary <- missing_data %>% 
  group_by(area, wood_collect_2level) %>% 
  summarize(n = n()) %>% 
  group_by(area) %>% 
  mutate(total_n = sum(n),
         perc = n/total_n*100) %>% 
  select(area, wood_collect_2level, n, perc, total_n)
missing_summary

@@

# Impute missing data; m = 10 datasets (check % missing data and match)
imputed_data <- mice(selected_vars, m=10, maxit = 40,
                     method = c("polr", "logreg", "logreg", "logreg", "logreg",
                                "polr", "polr", "logreg", "logreg", "logreg",
                                "pmm", "pmm", "pmm", "polr", "pmm"))

write_rds(imputed_data, paste0(file_path, "Output/imputed_exposure_data_7may2020.rds"))

imputed_exposure_data <- read_rds(paste0(file_path, "Output/imputed_exposure_data_7may2020.rds"))

@@

# Using MAMI package, perform model averaging and selection
## Will take ~20 to 30 mins with 5 iterations and bootstrap
model_ave <- mami(imputed_data, missing.data = "imputed", model = "gaussian",
                  outcome = "log_pm_mean_sampling_period", 
                  method = "MA.criterion", criterion = "AIC", print.time = TRUE)

write_rds(model_ave, paste0(file_path, "Output/imputed_exposure_model_7may2020.rds"))

exposure_model <- read_rds(paste0(file_path, "Output/imputed_exposure_model_7may2020.rds"))

summary(test_model_results)

# plot(model_ave) # only used when bootstrap used in mami

print(exposure_model)
```
